Large and Infinitary Quotient Inductive-Inductive Types

### 2020-01-10 draft/paper.tex
paper

We can convert a signature to a syntactic one by interpreting it in some
$\syn_j$ model, and we can convert in the other direction by using ToS-induction
to interpret a $\Gamma : \Con_{\syn_j}$ in an arbitrary ToS model.

>>>>

We can convert a signature to a syntactic one by interpreting it in $\syn_j$,
and we can convert in the other direction by using ToS-induction to interpret a
$\Gamma : \Con_{\syn_j}$ in an arbitrary ToS model.
